An Overview of Distributed Version Control Systems

### 2010-09-08 laarsample.tex
Corregida la redaccion de un parrafo de la conclusion

%----------------------------------------------------------------------
% SECTION II: Architecture
1%----------------------------------------------------------------------
\section{ARCHITECTURE}
\label{ARCHITECTURE}

@@

% Re-redactar el paréntesis que está confuso
Distributed versioning \emph{is} more complex, and there is a ``conceptual overhead'' in the usage 
of it, even if most of the time you can ignore most features and use just what you need 
(even for one person proyects, Git and Mercurial may be easier to use than SVN).

>>>>

%----------------------------------------------------------------------
% SECTION II: Architecture
%----------------------------------------------------------------------
\section{ARCHITECTURE}
\label{ARCHITECTURE}

@@

% Re-redactar el paréntesis que está confuso
Distributed versioning \emph{is} more complex, and there is a ``conceptual overhead'' in the usage 
of it, even if most of the time you can ignore most features and use just what you need. However for one person proyects, 
Git and Mercurial might be easier to use than SVN.
